# Work Plan (Gantt Chart) {#workplan}

```{r gantt-table, include=TRUE, echo=FALSE}

netpyne_gantt <- tibble::tribble(~wp, ~activity, ~start_date, ~end_date,
                                "WP1: AdEx in NEURON", "Analize previous Adex model", "22-03-01", "22-03-25", 
                                "WP1: AdEx in NEURON", "(Re) Implement Adex model in NEURON", "22-03-28", "22-04-29",
                                "WP1: AdEx in NEURON", "Replicate figures from Naudi et al.", "22-05-02", "22-06-03",
                                "WP2: AdEx in NetPyNe", "Incorporate AdEx into NetPyNe", "22-06-06", "22-06-24",
                                "WP2: AdEx in NetPyNe", "Replicate Izhikevic tutorial with AdEx", "22-06-24", "22-07-08",
                                "WP3: Documentation", "Document Process", "22-03-01", "22-08-08",
                                "WP3: Documentation", "Write AdEx Tutorial for NetPyne", "22-06-06", "22-07-29",
                                "Internship","RIKEN Summer Program","22-06-15","22-08-30") 

netpyne_spots <- tibble::tribble(~activity, ~spot_type, ~spot_date,
                                         "Internship","E","22-03-20",
                                         "Document Process", "D", "22-03-31",
                                         "Document Process", "D", "22-04-28",
                                         "Document Process", "D", "22-05-26",
                                         "Document Process", "D", "22-06-30",
                                         "Write AdEx Tutorial for NetPyne", "M", "22-07-21")

knitr::kable(netpyne_gantt)
```

```{r gantt, include=TRUE, echo=FALSE}
ganttrify(project = netpyne_gantt,
          spots = netpyne_spots,
          by_date = TRUE,
          exact_date = TRUE,
          size_text_relative = 0.8, 
          month_number_label = TRUE,
          hide_wp = FALSE)
```

## WP1: AdEx in NEURON

1. I will first *analyze the AdEx.mod file/model* based on what Kerr Lab did previously. This particular file has the characteristic that it kindda implement some Point Process that could might be useful for the Adex.

2. After the code is understood, I will re-implement the model and make some parametrization and test the firing in NEURON.

3. With the previous **working** adex model, I will replicate the different behavior that is shown in the Naud paper[@naud2008firing]

## WP2: AdEx in NetPyNe

1. Assuming that adex.mod is working in NEURON, I will then plug it into NetPyNe. First, I will do a simple single spiking neuron. Then, I will test a network of AdEx neurons.

2. Finally, and for a proper implementation and documentation of the model, I will replicate and write a new tutorial, based on the [Izhikevic](http://www.netpyne.org/tutorial.html?highlight=izhike#tutorial-4-using-a-simplified-cell-model-izhikevich) one

## WP3: Documentation

During the whole project, I will be writting and documenting every step. This process will be shown in this Lab Notebook.

## Project's key activities

**D**eliverables: Montly meeting update.

**M**ilestone: Full project presentation (labmeeting).

**E**vent: Result from RIKEN
